---
title: "Sightseeing with leaflet"
author: "Sofie Frederiksen"
output: 
  html_document:
    toc: true
    toc_float: true
date: "2022-12-05"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r installing the libraries, include=FALSE}
library(leaflet)
library(htmlwidgets)
library(tidyverse)
library(googlesheets4)
library(leaflet)
gs4_deauth()
```


# the code used for australia
This is just to show where I got my coding to Denmark from, it can be ignored
```{r}
# First, create labels for your points
popup = c("Robin", "Jakub", "Jannes")

# You create a Leaflet map with these basic steps: you need to run the whole chain of course
leaflet() %>%                                 # create a map widget by calling the library
  addProviderTiles("Esri.WorldPhysical") %>%  # add Esri World Physical map tiles
  addAwesomeMarkers(lng = c(-3, 23, 11),      # add layers, specified with longitude for 3 points
                    lat = c(52, 53, 49),      # and latitude for 3 points
                    popup = popup)            # specify labels, which will appear if you click on the point in the map


### Let's look at Sydney with setView() function in Leaflet
leaflet() %>%
  addTiles() %>%                              # add default OpenStreetMap map tiles
  addProviderTiles("Esri.WorldImagery",       # add custom Esri World Physical map tiles
                   options = providerTileOptions(opacity=0.5)) %>%     # make the Esri tile transparent
  setView(lng = 151.005006, lat = -33.9767231, zoom = 10)              # set the location of the map 


# Now let's refocus on Europe again
leaflet() %>% 
  addTiles() %>% 
  setView( lng = 2.34, lat = 48.85, zoom = 5 ) %>%  # let's use setView to navigate to our area
  addProviderTiles("Esri.WorldPhysical", group = "Physical") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Aerial") %>% 
  addProviderTiles("MtbMap", group = "Geo") %>% 

addLayersControl(                                 # we are adding layers control to the maps
  baseGroups = c("Geo","Aerial", "Physical"),
  options = layersControlOptions(collapsed = T))

# click the box in topright corner in your Viewer 
# to select between different background layers


########## SYDNEY HARBOUR DISPLAY WITH LAYERS
# Let's create a more complicated map 

# Set the location and zoom level
leaflet() %>% 
  setView(151.2339084, -33.85089, zoom = 13) %>%
  addTiles()  # checking I am in the right area


# Bring in a choice of esri background layers  

# Create a basic basemap
l_aus <- leaflet() %>%   # assign the base location to an object
  setView(151.2339084, -33.85089, zoom = 13)

# Now, prepare to select backgrounds
esri <- grep("^Esri", providers, value = TRUE)

# Select backgrounds from among provider tiles. To view them the options, 
# go to https://leaflet-extras.github.io/leaflet-providers/preview/
for (provider in esri) {
  l_aus <- l_aus %>% addProviderTiles(provider, group = provider)
}
l_aus

### Map of Sydney, NSW, Australia
# We make a layered map out of the components above and write it to 
# an object called AUSmap
AUSmap <- l_aus %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
addControl("", position = "topright")

# run this to see your product
AUSmap
```
# The code used for Denmark
## task 1: create a Danish equvalent of AUSmap
```{r my coordinates Create a Danish equivalent of AUSmap with esri layers,}

l_dk<- leaflet()%>%
  setView(10.3835473, 55.3997445, zoom = 20)

```
i chose the coordinates for rigsarkivet in Odense as I have been spending a lot of time there this term, but I added the coordinates for Odense Domkirke as that might interest others

```{r select the backgrounds}
# Now, prepare to select backgrounds
esri <- grep("^Esri", providers, value = TRUE)

# Select backgrounds from among provider tiles. To view them the options, 
# go to https://leaflet-extras.github.io/leaflet-providers/preview/ for (provider in esri) {
  l_dk <- l_dk %>% addProviderTiles(provider, group = provider)

l_dk
```


```{r create Danmap}
Danmap <- l_dk %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")

Danmap
```
It turns grey and I dont know why.



# ADD DATA TO LEAFLET

In this section you will manually create machine-readable spatial data from GoogleMaps: 

First, go to https://bit.ly/CreateCoordinates1
Enter the coordinates of your favorite leisure places in Denmark extracting them from the URL in googlemaps, adding name and type of monument.
Remember to copy the coordinates as a string, as just two decimal numbers separated by comma. 

Caveats: Do NOT edit the grey columns! They populate automatically!

Second, read the sheet into R. You will need gmail login information. 
watch the console, it may ask you to authenticate or put in the number 
that corresponds to the account you wish to use.

## Task 2: Read in the googlesheet data you and your colleagues populated with data into the DANmap object you created in Task 1.

```{r google sheets}
# Read in a Google sheet
places <- read_sheet("https://docs.google.com/spreadsheets/d/1PlxsPElZML8LZKyXbqdAYeQCDIvDps2McZx1cTVWSzI/edit#gid=124710918",
                     col_types = "cccnncnc", range="SA2022")
glimpse(places)
```
see the above and try and zoom in and out it makes it cleare

## Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet" and Task 5: Find out how to display notes and classifications in the map.

popup = paste(places$Placename, places$Description, places$Stars1_5), this code can be used if you dont want linechange between the different informations
you add notes and classification with the popup function 
```{r clustering}
# load the coordinates in the map and check: are any points missing? Why?
leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = paste(places$Placename,'<br>', places$Description,'<br>', places$Stars1_5),
             clusterOptions = markerClusterOptions())

```


Task 4: Look at the map and consider what it is good for and what not.
it began with the place description being the first thing you saw in the marker, but i didnt like that so i changed it. You also cant see the categories to what the things in the marker means like the numbers and so 


